\Title

### 2016-02-21 manuscript/manuscript.tex
Paragraph describing simple model and data

%\documentclass[]{article}
%\usepackage{natbib}
\documentclass[extra,mreferee]{gji}
% \documentclass[extra]{gji}
\usepackage{timet}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{url}
\usepackage[utf8]{inputenc}

@@

We have applied

>>>>

%\documentclass[]{article}
%\usepackage{natbib}
% \documentclass[extra,mreferee]{gji}
\documentclass[extra]{gji}
\usepackage{timet}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{url}
\usepackage[utf8]{inputenc}

@@

We simulate the transition from a continental-type Moho to an oceanic-type Moho
using a model composed of $M_{lat} \times M_{lon} = 40 \times 50$ grid of
juxtaposed tesseroids (a total of $M = 2000$ model elements).
The anomalous Moho density-contrast is $\Delta\rho = 400\ kg/m^3$
and the Normal Earth Moho depth is $z_{ref} = 30\ km$.
Fig.~\ref{fig:simple-data}a shows the model Moho depths,
where each pixel in the pseudo-color image corresponds to
a tesseroid of the model.

The synthetic data were forward modeled on a regular grid of
$N_{lat} \times N_{lon} = 79 \times 99$ points
(a total of $N = 7821$ observations)
at a constant height of 50 km.
The data were contaminated with pseudo-random noise
sampled from a normal distribution with zero mean and 5 mGal standard deviation.
Fig.~\ref{fig:simple-data}b shows the noise-corrupted full synthetic data set.
The data grid spacing is half the grid spacing of the tesseroid model
so that, when separating the training and testing data sets
(Fig.~\ref{fig:grid_separation}),
the training data set points will fall directly above each model element.
